---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# COVID-19 and mental health

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

*This project was done as part of [Barcelona GSE Masters Program in Data Science](https://www.barcelonagse.eu/study/masters-programs/data-science-methodology).*

## Overview

This app provides a striaght-forward interface for users to monitor COVID-19 and its potential effect on mental health across the world. It provides a general overview of current COVID case numbers and relates them to tweets streamed in real-time that relate to mental health.

## Usage

The app is hosted on shinyapps.io. Due to usage limits the server may not always be responsive. A more robust way to access the app is through Docker. To use the Docker image run:

```
docker run -d --name covid --net host patalt/covid_mental_health
```

### Install as R package

In case unfamiliar with Docker some users may prefer to install the app as an R package and run it through R Studio. To do so first install and attach the package through:

```{r, eval=F}
devtools::install_git(url = "https://github.com/pat-alt/covidMentalHealth.git", branch = "main")
library(covidMentalHealth)
```

Then simply run `run_app()` to run the Shiny app. 

### R and Python integration

The app relies on both R and Python code. The latter is integrated through [reticulate](https://rstudio.github.io/reticulate/). The app looks for the Python version found on your `PATH` through `reticulate::use_python(Sys.which("python"))`. Python dependencies are imported on load. In case you are missing any of the dependencies on your machine you can install them through `covidMentalHealth::install_py_dependencies()`.

## Data

We source data from two different APIs: for COVID case numbers we use [https://covid19-api.org/](https://covid19-api.org/) which continuously collects case numbers at country level from across the globe; for tweets we user Twitter streaming API. COVID data is sourced from the API a few times every day. Tweets are streamed continuously. We filter tweets that involve at least on term from this list related to mental health `["mental health","suicide","depression","anxiety"]` *and* at least one term from this list related to COVID `['covid','coronavirus','sars-cov-2','pandemic']`. 
